An Abstraction-based Approach to Network Synthesis

### 2016-11-03 paper/abstraction/paper.tex
temp commit

\section{Background and Motivation}
\label{sec:motivation}

@@

\paragraph*{Background}  Traditional routers use 
distributed protocols to exchange messages about available routes. 
One such protocol is the Border Gateway Protocol (BGP).  BGP is the
standard for inter-domain routing (the act of exchanging routing information 
between independently-owned networks) and is also commonly used in
data centers because it allows operators to define relatively flexible
routing policy while also scaling effectively to large networks.
When used within a data center, each router is configured with its own \emph{AS number},
which identifies it.

Each BGP message (also called a \emph{route announcement}) contains a 
\emph{destination prefix}, such as 10.1.1.0/24,\footnote{An address
such as 10.1.1.0 is 32 bits, with each of the four values representing 8 bits.  
A prefix such
as 10.1.1.0/24 denotes the set of addresses that begin with the first
24 bits of 10.1.1.0, \IE, all addresses that begin with 10.1.1.} as well as an
\emph{AS path}, such as XYZ (where each of X, Y and Z would be an AS number).  
Such messages indicate that the set of addresses
denoted by the prefix may be reached by following the path XYZ. 
A BGP message may also contain additional attributes, such as 
\emph{local preference} attribute and one or more
\emph{community values}.

A BGP router may receive messages about the same prefix from several
of its \emph{peers} (\IE, neighbouring routers).  When this occurs,
it processes the messages as follows:
\begin{enumerate}
\item It \emph{filters} (drops) some of the incoming messages based on
any their attributes (AS path, community values, peer it came from, \ETC),
and optionally modifies attributes of the messages it does not drop.
This is usually called the \emph{import} stage.
\item From the remaining messages, it selects the one message it
most \emph{prefers}. Selection is based on a number of criteria, but the
most important is the local preference number: Higher local preferences
are preferred.  Ties are broken by AS path length --- BGP defaults to 
shortest path routing in such cases.
\item Finally, it \emph{exports} the preferred message to selected neighbors,
adding its own AS number to the path and optionally adding or
modifying attributes.
\end{enumerate}
When a BGP router is configured, the user tunes the import and export
stages of the above process, choosing which messages to import, how to
modify them and how to export them.  By modifying the local preferences
on messages in the inport phase, the user determines which messages will
be selected.  This in turn determines how traffic destined for the given
address will be routed.  Keep in mind that if BGP messages to a destination
are propagated in one direction (left-to-right), then traffic will wind
up flowing in the opposite direction (right-to-left).

Rather than export 2$^n$ addresses in the same range, routers will
often perform \emph{route aggregation}, and export a single (32-$n$)-bit
prefix.  During aggregation, whenever an advertisement for 
\emph{any} of the 2$^n$ addresses
reaches the router, the \emph{entire} aggregate prefix will be announced.
While useful for decreasing announcements and avoiding churn, such
aggregation can be dangerous:  If a message for one of the 2$^n$ addresses (X)
reaches the aggregation router, but another one of the addresses (Y)
cannot reach the aggregation router due to a failure then the aggregate
will be announced, possibly drawing traffic to Y, even though Y cannot be
reached.  This is known as an \emph{aggregation-induced black hole}~\cite{route-aggregation}.
Networks should be configured to be sufficiently fault tolerant to minimize
the chances of such black holes.

\paragraph*{An Example}
%We motivate \sysname using an example data center network. Our network, 
Consider the data center network shown in Figure~\ref{fig:example}.  The boxes in the diagram
represent \emph{switches}, and these switches play several different roles:  T[1--8] denote top-of-rack (ToR) switches, A[1--8] denote aggregation switches, and S[1--2] denote spine switches. The spine switches are connected to the
rest of the internet; any traffic to or from the outside world flows through them.  The aggregation switches
serve as a bridge between spine and ToR switches.   Finally, each ToR switch is
connected to a set servers (``a rack''): P[1--8] denote groups of addresses for services hosted in each rack. 
% Such groups are called address {\em prefixes} because they are encoded using the adresses' shared prefix.

>>>>

\section{Background}
\label{sec:background}

In this work, we focus on synthesizing configurations for a network that runs the Border Gateway Protocol (BGP), which is the standard for routing across independent organizations and inside large datacenters. It scales effectively and allows operators to define flexible policies.

The interactions among BGP routers determines how the network forwards traffic. To invite traffic from a neighbor to a destination, routers announce the destination's address {\em prefix} (e.g., 10.1.1.0/24\footnote{An IP(v4) address
such as 10.1.1.0 is 32 bits, with each of the four values representing 8 bits. A prefix such as 10.1.1.0/24 denotes the set of addresses that share the first 24 bits with 10.1.1.0, \IE, all addresses that begin with 10.1.1.}) to the neighbor. In this way, traffic flows in the opposite direction to such {\em route announcements.}

Route announcements contain additional attributes. A common one is {\em AS path}, which denotes the sequence of Autonomous Systems that will be traversed to reach the destination. When BGP is used inside a datacenter, each router tends to be its own AS. Optional attributes include one or more {\em communities}, which are arbitrary strings. Operators agree on what each community value means out of band.

A BGP router may receive one or more announcements from different neighbors for the same prefix. It selects the best one(s) based on its {\em import policy}. These policies are a function of the AS path, community values, or the neighbor that sent the announcement, and may even filter some announcements altogether (i.e., not use them even if no other announcements to the destination are available). Then, based on the {\em export policy}, the router announces the selected route to one or more neighbors, after adding itself to the AS path and, optionally, modifying the set of community values.

%When this occurs,
%it processes the messages as follows:
%\begin{enumerate}
%\item It \emph{filters} (drops) some of the incoming messages based on
%any their attributes (AS path, community values, peer it came from, \ETC),
%and optionally modifies attributes of the messages it does not drop.
%This is usually called the \emph{import} stage.
%\item From the remaining messages, it selects the one message it
%most \emph{prefers}. Selection is based on a number of criteria, but the
%most important is the local preference number: Higher local preferences
%are preferred.  Ties are broken by AS path length --- BGP defaults to
%shortest path routing in such cases.
%\item Finally, it \emph{exports} the preferred message to selected neighbors,
%adding its own AS number to the path and optionally adding or
%modifying attributes.
%\end{enumerate}
%When a BGP router is configured, the user tunes the import and export
%stages of the above process, choosing which messages to import, how to
%modify them and how to export them.  By modifying the local preferences
%on messages in the inport phase, the user determines which messages will
%be selected.  This in turn determines how traffic destined for the given
%address will be routed.  Keep in mind that if BGP messages to a destination
%are propagated in one direction (left-to-right), then traffic will wind
%up flowing in the opposite direction (right-to-left).

A BGP router may also perform {\em route aggregation} when exporting to certain neighbors. That is, instead of announcing multiple prefixes it may announce a single covering prefix (e.g., 10.1.0.0/16 instead of 10.1.[1--255].0/24). The covering prefix is announced as long as the router has a valid route to any of the covered prefixes. Aggregation helps reduce the memory consumption of routers, but it can lead to traffic black holes~\cite{route-aggregation}. A router that announces 10.1.0.0/16, because it has a route to 10.1.1.0/24, may also get traffic for 10.1.2.0/24 to which it has no route.

%Rather than export 2$^n$ addresses in the same range, routers will
%often perform \emph{route aggregation}, and export a single (32-$n$)-bit
%prefix.  During aggregation, whenever an advertisement for
%\emph{any} of the 2$^n$ addresses
%reaches the router, the \emph{entire} aggregate prefix will be announced.
%While useful for decreasing announcements and avoiding churn, such
%aggregation can be dangerous:  If a message for one of the 2$^n$ addresses (X)
%reaches the aggregation router, but another one of the addresses (Y)
%cannot reach the aggregation router due to a failure then the aggregate
%will be announced, possibly drawing traffic to Y, even though Y cannot be
%reached.  This is known as an \emph{aggregation-induced black hole}~\cite{route-aggregation}.
%Networks should be configured to be sufficiently fault tolerant to minimize
%the chances of such black holes.

\section{Motivation}
\label{sec:motivation}

Configuring a BGP network requires configuring, among other things, the import and export policies for each router such that traffic flows in a way that is compliant with the network's global policies. We demonstrate the difficulty of this task using an example.

@@

Consider the data center network in Figure~\ref{fig:example}. The boxes in the diagram
represent \emph{switches}. Using terminology for fat tree networks~\cite{fattree}, T[1--8] denote top-of-rack (ToR) switches, A[1--8] denote aggregation switches, and S[1--2] denote spine switches. The spine switches are connected to the
rest of the Internet; any traffic to or from the outside world flows through them.  The aggregation switches 
bridge the spines to the ToRs which attach to a set of servers (``a rack''). P[1--8] denote address prefixes for services hosted in each rack.
